Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-07-15 Manuscript/main.tex
Worked on partial effects plots

Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
In commodity fields, honey bee visitation decreased from 8.5 visits/hr at the edge of the field to 3.1 visits/hr at 100 m into the field (p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}, given a stocking rate of 20 hives).
% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015. % (at a stocking level of 20 hives). 
Higher stocking rates increased honey bee visitation at the edge of the field from 14.5 visits/hr with an apiary of 20 hives to 22.7 visits/hr with an apiary of 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 1.8 visits/hr.
Honey bee visitation was much higher overall in seed canola fields, but still decreased from 126 visits/hr at edge of field to 78 visits/hr at 100 m from the apiary (Z=-2.5, p$=$0.01). 
Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).

>>>>

Honey bee visitation decreased with distance away from the apiary, in both commodity and seed canola fields.
In commodity fields, honey bee visitation decreased from 6.4 visits/hr at the edge to 1.0 visits/hr at the centre of the field (400 m) (p$=$0.0002, Figure \ref{fig:hbeeDist_commodity}, apiary of 40 hives).
% Visitation rates were higher in both years in Lethbridge (2014: 9.3 visits/hr, 2015: 7.1), but were higher in 2015 than 2014 at Grande Prairie (Z=2.3, p$=$0.02), rising from 5 visits/hr at the field edge in 2014 to 17 visits/hr in 2015. % (at a stocking level of 20 hives). 
Higher stocking rates increased honey bee visitation at the edge of the field from 3.9 visits/hr with an apiary of 20 hives, increasing to 6.4 visits/hr with 40 hives (Z=5.3, p$<$0.0001), while unstocked field edges had an average of 0.4 visits/hr.
Honey bee visitation was much higher overall in seed canola fields, and decreased from 99.5 visits/hr at edge to 78.8 visits/hr at the centre of the field (Z=-2.5, p$=$0.01). 
Honey bee visitation was also lower near leafcutter shelters (Z=3.9, p$=$0.001), dropping from 60 visits/hr at 10 m to 34 visits/hr at 2 m, likely due to competition with LCBs (Figure \ref{fig:hbeeDist_both}, \ref{fig:lbeeDist_both}).
